Classifying Protein Secondary Structures through Deep Network Learning

### 2013-12-18 docs/paper.tex
ROC curve all in one
Fix weblink in reference

% describe results
% Insert and discuss ROC curves -- should I put ALPHA, BETA, LOOP on one plot?
% combine into 1????
\begin{figure}[ht!]
\centering
\includegraphics[width=65mm]{results/ROC_ALPHA.png}
\caption{}
\label{fig:roc_alpha}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[width=65mm]{results/ROC_BETA.png}
\caption{}
\label{fig:roc_beta}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[width=65mm]{results/ROC_LOOP.png}
\caption{}
\label{fig:roc_loop}
\end{figure}

@@

\bibitem{uci}
   C.L. Blake and C.J. Merz,
   `` UCI repository of machine learning databases"
   \textbf{http://archive.ics.uci.edu/ml/datasets/Molecular+Biology+(Protein+Secondary+Structure)}

>>>>

% describe results
% Insert and discuss ROC curves -- should I put ALPHA, BETA, LOOP on one plot?
% combine into 1????
\begin{figure}[ht!]
\centering
\includegraphics[width=65mm]{results/ROC_all.png}
\caption{}
\label{fig:roc}
\end{figure}

@@

\bibitem{uci}
   C.L. Blake and C.J. Merz,
   `` UCI repository of machine learning databases"
   \textbf{http://archive.ics.uci.edu/ml/datasets/}
   \textbf{Molecular+Biology+(Protein+}
   \textbf{Secondary+Structure)}
